### 2020-04-02 scache/jpdc/tex/impl.tex
some minor fixes

When a DAG job is submitted, the DAG information is generated in the framework task scheduler. 
% Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
% For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
If the RangePartitioner or a customized non-hash partitioner is used, SCache will insert an extra sampling job before the job starts.
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
SCache master predicts the reduce partition size based on the data and then call Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
{\color{black}
SCache uses bellowed memory management to ensure performance.
If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
}

>>>>

When a DAG job is submitted, the DAG information is generated in the framework task scheduler. 
% Before the computing tasks begin, the shuffle dependencies are determined based on DAG.
% For each shuffle dependency, the shuffle ID, the type of partitioner, the number of map tasks, and the number of reduce tasks are included.
If the RangePartitioner or a customized non-hash partitioner is used, SCache will insert an extra sampling job before the job starts.
The sampling job uses a reservoir sampling algorithm \cite{reservoir} on each partition to gather the sample data.
SCache master predicts the reduce partition size based on the data and then \edited{calls} Algorithm \ref{hminheap} or \ref{mhminheap} to do the pre-scheduling.

@@

\subsection{Memory Management}\label{memorymanage}
% As mentioned in Section \ref{observation}, though the shuffle size is relatively small, memory management should still be cautious enough to limit the effect of performance of DAG framework.
{\color{black}
SCache uses \edited{memory management described below} to ensure performance.
If the reserved memory is running out, SCache will flush some of the blocks into the disk temporarily and then re-fetch them if needed.
SCache leverages two constraints to manage the shuffle blocks: \textit{all-or-nothing} and \textit{context-aware-priority}.
% When the size of cached blocks reaches the limit of reserved memory, SCache flushes some of them to the disk temporarily, and re-fetches them when some cached shuffle blocks are consumed or pre-fetched. 
% To achieve the maximum overall improvement, SCache leverages two constraints to manage the in-memory data --- \textit{all-or-nothing} and \textit{context-aware-priority}.
}

### 2020-04-02 scache/jpdc/tex/model.tex
some minor fixes

% The FRQ model uses these overlaps to describe different scheduling strategies.
{\color{black}
Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
The FRQ model needs to know the start time of each phases.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
}

@@

	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} shown, the shuffle phase will be interrupted in each round. In this case, the formula of \(T_{P\_Shuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

>>>>

% The FRQ model uses these overlaps to describe different scheduling strategies.
{\color{black}
Besides, the FRQ model also needs to input the scheduling strategies the framework takes.
The FRQ model needs to know the start time of each \edited{phase}.
For example, as shown in Figure \ref{fig:model_hadoop}, this strategy starts the shuffle phase and the reduce phase at the same time.
And Figure \ref{fig:model_basic} shows the pre-fetching strategy used by SCache. In the pre-fetching strategy, the shuffle phase starts as soon as it can in the map phase.
}

@@

	When the shuffle speed (\(V_{Shuffle}\)) is faster, SCache needs to wait for shuffle data to be generated. As Figure \ref{fig:model_scache2} \edited{shows}, the shuffle phase will be interrupted in each round. In this case, the formula of \(T_{P\_Shuffle}\) is as followed:
	\begin{equation}
		\label{equation_Tpshuffle2}
		\begin{aligned}
			T_{P\_Shuffle} &= T_{Shuffle} \times \frac{1}{N}
		\end{aligned}
	\end{equation}
\end{enumerate}

### 2020-04-02 scache/jpdc/tex/optimization.tex
jpdc
some minor fixes

\begin{figure}
	% \centering
	% \begin{subfigure}[b]{0.31\linewidth}
		% 	\includegraphics[width=\linewidth]{fig/hash_pre}
		% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
		% 	\label{fig:hash_pre}
	% \end{subfigure}
	\begin{subfigure}[b]{0.5\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
		% \vspace{1em}
	\end{subfigure}
	\begin{subfigure}[b]{0.49\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	% \vspace{-1em}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=.6\linewidth]{fig/sim} % second figure itself
	\caption{Stage Completion Time Improvement of OpenCloud Trace}
	\label{fig:sim}
\end{figure}

@@

SCache caches the shuffle data on the memory instead of storing on disk liked Spark or Hadoop MapReduce.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.

>>>>

\begin{figure}
	\centering
	% \begin{subfigure}[b]{0.31\linewidth}
		% 	\includegraphics[width=\linewidth]{fig/hash_pre}
		% 	\caption{Linear Regression Prediction of Hash Partitioner\newline}
		% 	\label{fig:hash_pre}
	% \end{subfigure}
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{fig/range_pre_sample}
		\caption{Linear Regression and Sampling Prediction of Range Partitioner}
		\label{fig:range_pre_sample}
		% \vspace{1em}
	\end{subfigure}
	\begin{subfigure}{0.75\linewidth}
		\includegraphics[width=\linewidth]{fig/prediction_relative_error}
		\caption{Prediction Relative Error of Range Partitioner\newline}
		\label{fig:prediction_relative_error}
	\end{subfigure}
	\caption{Reduction Distribution Prediction}
	\label{fig:dis}
	% \vspace{-1em}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.75\linewidth]{fig/sim} % second figure itself
	\caption{Stage Completion Time Improvement of OpenCloud Trace}
	\label{fig:sim}
\end{figure}

@@

SCache caches the shuffle data on the memory instead of storing on disk \edited{like} Spark or Hadoop MapReduce.
In this aspect, SCache optimizes the time of shuffle read and shuffle write since memory gets better I/O performance.
}
% To achieve the decoupling of map tasks and reduce tasks, the original shuffle write and read implementation in the current frameworks should be modified to apply the API of SCache.
% To prevent the release of a slot being blocked by shuffle write,  
% SCache provides a disk-write-like API named $putBlock$ to handle the storage of partitioned shuffle data blocks produced by a map task.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks to SCache's reserved memory and release the slot immediately.
% Inside the $putBlock$, SCache uses memory copy to move the shuffle data blocks out of map tasks and store them in the reserved memory.
% After the memory copy, the slot will be released immediately.
